Location and Scale-Invariant Power Transformations for Transforming Data to Normality

### 2025-10-29 manuscript_latex/manuscript.tex
Update appendix e.

\begin{table}
\caption{Residual errors for features from real-world datasets after Yeo-Johnson transformation to normality.
Several transformation methods include normalisation before transformation, indicated by z-score normalisation (norm.) or robust scaling.
AWT: arterial wall thickness; FE: fuel efficiency; PBM: penguin body mass}
\label{tab:experimental-results-appendix-residuals}
\begin{tabular}{l | r r r r r}

@@

\midrule
none                                  & 16.5 & 110.1 & 54.5 & 328.4 & 48.0 \\
conventional                          & 11.5 &  30.0 & 55.3 & 319.0 & 32.2 \\
conventional (z-score norm.)          & 11.5 &  19.3 & 49.0 & 326.2 & 33.3 \\
conventional (robust scaling)         & 11.3 &  31.8 & 53.3 & 324.5 & 32.2 \\
Raymaekers-Rousseeuw                  & 11.5 & 136.7 & 47.7 & 315.1 & 32.2 \\
Raymaekers-Rousseeuw (z-score norm.)  & 13.2 & 214.5 & 57.4 & 326.2 & 33.3 \\
Raymaekers-Rousseeuw (robust scaling) & 11.7 & 281.3 & 57.0 & 324.5 & 32.0 \\
invariant                             &  8.8 &  12.2 & 44.0 & 326.4 & 26.8 \\
robust invariant                      &  9.3 &  30.2 & 55.8 & 308.1 & 22.0 \\

\bottomrule
\end{tabular}
\end{table}

\begin{table}
\caption{Transformation parameter $\lambda$ for features from real-world datasets after Yeo-Johnson transformation to normality.
Several transformation methods include normalisation before transformation, indicated by z-score normalisation (norm.) or robust scaling.
AWT: arterial wall thickness; FE: fuel efficiency; PBM: penguin body mass}
\label{tab:experimental-results-appendix-lambda}
\begin{tabular}{l | r r r r r}

@@

\midrule
conventional                          & 2.0 & -0.7 & -0.1 & 62.1 & -0.5 \\
conventional (z-score norm.)          & 1.2 & -1.7 & -0.1 &  1.3 &  0.6 \\
conventional (robust scaling)         & 1.3 &  0.0 &  0.2 &  1.4 &  0.4 \\
Raymaekers-Rousseeuw                  & 2.0 &  1.1 &  0.8 & 95.4 & -0.5 \\
Raymaekers-Rousseeuw (z-score norm.)  & 1.3 &  1.4 &  1.0 &  1.3 &  0.6 \\
Raymaekers-Rousseeuw (robust scaling) & 1.4 &  1.3 &  1.0 &  1.4 &  0.4 \\
invariant                             & 1.3 &  0.2 & -1.3 &  1.5 &  0.5 \\
robust invariant                      & 1.3 & -0.3 &  1.0 &  1.1 &  0.3 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}
\caption{
p-values of empirical central normality tests for features from real-world datasets after Yeo-Johnson transformation to normality.
Several transformation methods include normalisation before transformation, indicated by z-score normalisation (norm.) or robust scaling.
AWT: arterial wall thickness; FE: fuel efficiency; PBM: penguin body mass}
\label{tab:experimental-results-appendix-p-value}
\begin{tabular}{l | r r r r r}

@@

none                                  & 0.694 & 0.832     & 0.727     & $< 0.001$ & $< 0.001$ \\
conventional                          & 0.961 & 0.003     & $< 0.001$ & $< 0.001$ & 0.101 \\
conventional (z-score norm.)          & 0.919 & 0.021     & $< 0.001$ & $< 0.001$ & 0.099 \\
conventional (robust scaling)         & 0.933 & $< 0.001$ & $< 0.001$ & $< 0.001$ & 0.129 \\
Raymaekers-Rousseeuw                  & 0.961 & 0.881     & 0.373     & $< 0.001$ & 0.101 \\
Raymaekers-Rousseeuw (z-score norm.)  & 0.694 & 0.899     & 0.809     & $< 0.001$ & 0.099 \\
Raymaekers-Rousseeuw (robust scaling) & 0.900 & 0.880     & 0.811     & $< 0.001$ & 0.144 \\
invariant                             & 0.976 & 0.147     & $< 0.001$ & $< 0.001$ & 0.276 \\
robust invariant                      & 0.933 & 0.178     & 0.759     & $< 0.001$ & 0.688 \\

\bottomrule
\end{tabular}
\end{table}

@@

\begin{table}
\caption{Residual errors for features from real-world datasets after Box-Cox transformation to normality.
Several transformation methods include normalisation before transformation, indicated by z-score normalisation (norm.) or robust scaling.
AWT: arterial wall thickness; FE: fuel efficiency; PBM: penguin body mass}
\label{tab:experimental-results-appendix-residuals-bc}
\begin{tabular}{l | r r r r r}

@@

\midrule
none                                  & 16.5 & 110.1 &  54.5 & 328.4 & 48.0 \\
conventional                          & 11.5 &  33.5 &  55.7 & 318.9 & 32.2 \\
conventional (z-score norm.)          & 12.9 &  44.5 &  58.8 & 305.3 & 27.3 \\
conventional (robust scaling)         & 12.9 &  44.7 &  59.0 & 305.3 & 27.3 \\
Raymaekers-Rousseeuw                  & 11.5 & 127.1 &  47.6 & 314.8 & 32.2 \\
Raymaekers-Rousseeuw (z-score norm.)  & 13.1 &  54.8 & 127.5 & 510.2 & 23.6 \\
Raymaekers-Rousseeuw (robust scaling) & 18.9 & 100.2 & 113.7 & 510.2 & 23.6 \\
invariant                             & 11.6 &  28.0 &  48.4 & 311.8 & 27.3 \\
robust invariant                      & 12.8 & 150.1 &  60.5 & 646.0 & 27.4 \\

\bottomrule
\end{tabular}
\end{table}

\begin{table}
\caption{Transformation parameter $\lambda$ for features from real-world datasets after Box-Cox transformation to normality.
Several transformation methods include normalisation before transformation, indicated by z-score normalisation (norm.) or robust scaling.
AWT: arterial wall thickness; FE: fuel efficiency; PBM: penguin body mass}
\label{tab:experimental-results-appendix-lambda-bc}
\begin{tabular}{l | r r r r r}

@@

conventional                          & 1.9 & -0.5 & -0.1 & 62.1 & -0.5 \\
conventional (z-score norm.)          & 1.2 &  0.1 &  0.2 &  1.2 &  0.5 \\
conventional (robust scaling)         & 1.2 &  0.1 &  0.1 &  1.2 &  0.5 \\
Raymaekers-Rousseeuw                  & 1.9 &  1.1 &  0.8 & 95.9 & -0.5 \\
Raymaekers-Rousseeuw (z-score norm.)  & 1.2 &  0.6 & -0.5 &  0.6 &  0.3 \\
Raymaekers-Rousseeuw (robust scaling) & 0.9 &  1.0 & -0.5 &  0.6 &  0.3 \\
invariant                             & 1.7 & -1.0 & -0.7 &  1.9 &  0.5 \\
robust invariant                      & 1.3 &  1.2 &  1.1 &  0.4 &  0.1 \\

\bottomrule
\end{tabular}
\end{table}

\begin{table}
\caption{
p-values of empirical central normality tests for features from real-world datasets after Box-Cox transformation to normality.
Several transformation methods include normalisation before transformation, indicated by z-score normalisation (norm.) or robust scaling.
AWT: arterial wall thickness; FE: fuel efficiency; PBM: penguin body mass}
\label{tab:experimental-results-appendix-p-value-bc}
\begin{tabular}{l | r r r r r}

@@

none                                  & 0.694 & 0.832 & 0.727     & $< 0.001$ & $< 0.001$ \\
conventional                          & 0.961 & 0.002 & $< 0.001$ & $< 0.001$ & 0.101 \\
conventional (z-score norm.)          & 0.901 & 0.005 & $< 0.001$ & $< 0.001$ & 0.154 \\
conventional (robust scaling)         & 0.901 & 0.005 & $< 0.001$ & $< 0.001$ & 0.154 \\
Raymaekers-Rousseeuw                  & 0.961 & 0.871 & 0.365     & $< 0.001$ & 0.101 \\
Raymaekers-Rousseeuw (z-score norm.)  & 0.891 & 0.268 & $< 0.001$ & $< 0.001$ & 0.495 \\
Raymaekers-Rousseeuw (robust scaling) & 0.562 & 0.789 & $< 0.001$ & $< 0.001$ & 0.492 \\
invariant                             & 0.962 & 0.004 & $< 0.001$ & $< 0.001$ & 0.154 \\
robust invariant                      & 0.899 & 0.890 & 0.866     & $< 0.001$ & 0.622 \\

\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\begin{center}
\caption{Residual errors for features from real-world datasets after Yeo-Johnson transformation to normality.
Several transformation methods include normalisation before transformation, indicated by z-score normalisation (norm.) or robust scaling.
AWT: arterial wall thickness; FE: fuel efficiency; PBM: penguin body mass}
\label{tab:experimental-results-appendix-residuals}
\begin{tabular}{l | r r r r r}

@@

\midrule
none                                  & 16.5 & 110.1 & 54.5 & 328.4 & 48.0 \\
conventional                          & 11.5 &  30.0 & 55.3 & 319.0 & 32.2 \\
conventional (z-score norm.)          & 11.5 &  19.3 & 49.0 & 326.2 & 33.3 \\
conventional (robust scaling)         & 11.3 &  33.3 & 55.9 & 326.5 & 31.5 \\
Raymaekers-Rousseeuw                  & 11.5 & 136.7 & 47.7 & 315.1 & 32.2 \\
Raymaekers-Rousseeuw (z-score norm.)  & 13.2 & 214.5 & 57.4 & 326.2 & 33.3 \\
Raymaekers-Rousseeuw (robust scaling) & 13.4 & 202.9 & 56.9 & 326.4 & 31.5 \\
invariant                             &  8.8 &  12.2 & 44.0 & 326.4 & 26.8 \\
robust invariant                      &  9.3 &  30.2 & 55.8 & 308.1 & 22.0 \\

\begin{table}
\begin{center}
\caption{Transformation parameter $\lambda$ for features from real-world datasets after Yeo-Johnson transformation to normality.
Several transformation methods include normalisation before transformation, indicated by z-score normalisation (norm.) or robust scaling.
AWT: arterial wall thickness; FE: fuel efficiency; PBM: penguin body mass}
\label{tab:experimental-results-appendix-lambda}
\begin{tabular}{l | r r r r r}

@@

\midrule
conventional                          & 2.0 & -0.7 & -0.1 & 62.1 & -0.5 \\
conventional (z-score norm.)          & 1.2 & -1.7 & -0.1 &  1.3 &  0.6 \\
conventional (robust scaling)         & 1.2 &  0.0 &  0.3 &  1.3 &  0.6 \\
Raymaekers-Rousseeuw                  & 2.0 &  1.1 &  0.8 & 95.4 & -0.5 \\
Raymaekers-Rousseeuw (z-score norm.)  & 1.3 &  1.4 &  1.0 &  1.3 &  0.6 \\
Raymaekers-Rousseeuw (robust scaling) & 1.3 &  1.2 &  1.0 &  1.3 &  0.6 \\
invariant                             & 1.3 &  0.2 & -1.3 &  1.5 &  0.5 \\
robust invariant                      & 1.3 & -0.3 &  1.0 &  1.1 &  0.3 \\
\bottomrule
\end{tabular}
\end{center}
\end{table}

\begin{table}
\begin{center}
\caption{
p-values of empirical central normality tests ($\kappa = 0.80$) for features from real-world datasets after Yeo-Johnson transformation to normality.
Several transformation methods include normalisation before transformation, indicated by z-score normalisation (norm.) or robust scaling.
AWT: arterial wall thickness; FE: fuel efficiency; PBM: penguin body mass}
\label{tab:experimental-results-appendix-p-value}
\begin{tabular}{l | r r r r r}

@@

none                                  & 0.541 &    0.731  &    0.546  & $< 0.001$ & $< 0.001$ \\
conventional                          & 0.919 & $< 0.001$ & $< 0.001$ & $< 0.001$ &    0.032 \\
conventional (z-score norm.)          & 0.845 &    0.007  & $< 0.001$ & $< 0.001$ &    0.031 \\
conventional (robust scaling)         & 0.847 & $< 0.001$ & $< 0.001$ & $< 0.001$ &    0.063 \\
Raymaekers-Rousseeuw                  & 0.919 &    0.802  &    0.205  & $< 0.001$ &    0.032 \\
Raymaekers-Rousseeuw (z-score norm.)  & 0.540 &    0.830  &    0.655  & $< 0.001$ &    0.031 \\
Raymaekers-Rousseeuw (robust scaling) & 0.438 &    0.878  &    0.669  & $< 0.001$ &    0.064 \\
invariant                             & 0.947 &    0.071  & $< 0.001$ & $< 0.001$ &    0.123 \\
robust invariant                      & 0.867 &    0.091  &    0.587  & $< 0.001$ &    0.477 \\

@@

\begin{table}
\begin{center}
\caption{Residual errors for features from real-world datasets after Box-Cox transformation to normality.
Several transformation methods include normalisation before transformation, indicated by z-score normalisation (norm.) or robust scaling.
AWT: arterial wall thickness; FE: fuel efficiency; PBM: penguin body mass}
\label{tab:experimental-results-appendix-residuals-bc}
\begin{tabular}{l | r r r r r}

@@

\midrule
none                                  & 16.5 & 110.1 &  54.5 & 328.4 & 48.0 \\
conventional                          & 11.5 &  33.5 &  55.7 & 318.9 & 32.2 \\
conventional (z-score norm.)          & 12.9 &  44.5 &  58.8 & 305.3 & 27.3 \\
conventional (robust scaling)         & 12.9 &  44.7 &  59.0 & 305.3 & 27.3 \\
Raymaekers-Rousseeuw                  & 11.5 & 127.1 &  47.6 & 314.8 & 32.2 \\
Raymaekers-Rousseeuw (z-score norm.)  & 13.1 &  54.8 & 127.5 & 510.2 & 23.6 \\
Raymaekers-Rousseeuw (robust scaling) & 13.1 & 100.2 &  44.9 & 423.2 & 23.6 \\
invariant                             & 11.6 &  28.0 &  48.4 & 311.8 & 27.3 \\
robust invariant                      & 12.8 & 150.1 &  60.5 & 646.0 & 27.4 \\

\begin{table}
\begin{center}
\caption{Transformation parameter $\lambda$ for features from real-world datasets after Box-Cox transformation to normality.
Several transformation methods include normalisation before transformation, indicated by z-score normalisation (norm.) or robust scaling.
AWT: arterial wall thickness; FE: fuel efficiency; PBM: penguin body mass}
\label{tab:experimental-results-appendix-lambda-bc}
\begin{tabular}{l | r r r r r}

@@

conventional                          & 1.9 & -0.5 & -0.1 & 62.1 & -0.5 \\
conventional (z-score norm.)          & 1.2 &  0.1 &  0.2 &  1.2 &  0.5 \\
conventional (robust scaling)         & 1.2 &  0.1 &  0.1 &  1.2 &  0.5 \\
Raymaekers-Rousseeuw                  & 1.9 &  1.1 &  0.8 & 95.9 & -0.5 \\
Raymaekers-Rousseeuw (z-score norm.)  & 1.2 &  0.6 & -0.5 &  0.6 &  0.3 \\
Raymaekers-Rousseeuw (robust scaling) & 1.2 &  1.0 &  0.8 &  0.7 &  0.3 \\
invariant                             & 1.7 & -1.0 & -0.7 &  1.9 &  0.5 \\
robust invariant                      & 1.3 &  1.2 &  1.1 &  0.4 &  0.1 \\

\begin{table}
\begin{center}
\caption{
p-values of empirical central normality tests ($\kappa = 0.80$) for features from real-world datasets after Box-Cox transformation to normality.
Several transformation methods include normalisation before transformation, indicated by z-score normalisation (norm.) or robust scaling.
AWT: arterial wall thickness; FE: fuel efficiency; PBM: penguin body mass}
\label{tab:experimental-results-appendix-p-value-bc}
\begin{tabular}{l | r r r r r}

@@

none                                  & 0.541 &    0.731  &    0.546  & $< 0.001$ & $< 0.001$ \\
conventional                          & 0.919 & $< 0.001$ & $< 0.001$ & $< 0.001$ &    0.032 \\
conventional (z-score norm.)          & 0.815 &    0.001  & $< 0.001$ & $< 0.001$ &    0.057 \\
conventional (robust scaling)         & 0.815 &    0.001  & $< 0.001$ & $< 0.001$ &    0.057 \\
Raymaekers-Rousseeuw                  & 0.919 &    0.787  &    0.200  & $< 0.001$ &    0.032 \\
Raymaekers-Rousseeuw (z-score norm.)  & 0.799 &    0.152  & $< 0.001$ & $< 0.001$ &    0.285 \\
Raymaekers-Rousseeuw (robust scaling) & 0.799 &    0.674  &    0.060  & $< 0.001$ &    0.285 \\
invariant                             & 0.919 &    0.001  & $< 0.001$ & $< 0.001$ &    0.057 \\
robust invariant                      & 0.813 &    0.817  &    0.736  & $< 0.001$ &    0.403 \\
